```{r}
install.packages("microbenchmark")
library(microbenchmark)
```

#Q1: Problem 1 from Activity 9
** Original codes:**
```{r}
odd_count = function(x) {
  odd_num = 0
  for(i in 1:length(x)) {
    if(x[i] %% 2 == 1) 
      odd_num  = odd_num+1
  }
  return(odd_num)
}
```
**My codes: **
```{r}
odd_count_new = function(x) {
  return (sum(x %% 2))
}
```
**TEST: **
```{r}
x <- c(1,2,3,4,5,6,7,8,9)
odd_count(x)
odd_count_new(x)
microbenchmark(odd_count(x), odd_count_new(x))
```

#Q2: Modify sort_vect function:
Modify the sorting function (sort_vec) from "Assignment 8" (problem 3) so that it should take an
additional argument ascending which causes sorting in increasing order when 'ascending = TRUE'. In
other words,
. sort_vect(c(3, 1, 2), ascending = TRUE) = (1, 2, 3)
. sort_vect(c(3, 1, 2), ascending = FALSE) = (3, 2, 1)
```{r}
sort_vec = function(x, ascending) {
  
  if (length(x) < 2) return (x)
  if(ascending==TRUE){
    for(last in length(x):2) {
    for(first in 1:(last - 1)) {
      if(x[first] > x[first + 1]) {
        temp = x[first]
        x[first] = x[first + 1]
        x[first + 1] = temp
      }
    }
  }
  }else{
    for(last in length(x):2) {
    for(first in 1:(last - 1)) {
      if(x[first] < x[first + 1]) {
        temp = x[first]
        x[first] = x[first + 1]
        x[first + 1] = temp
      }
    }
  }
  }
  
return(x)
} 
##TEST:
test_sort <- c(3, 2, 1, 5, 4)
sort_vec(test_sort, TRUE)
sort_vec(test_sort, FALSE)
```
#Q3: 
Consider a simple random walk with starting point 0 and a step -1 or 1. Below is the code with
dynamically allocated memory. Write your code with preallocated memory and compare time for both
versions using system.time() function (use N = 1000, 10000 and 1000000).
```{r}
#Given Codes:
test_original_codes <- function(N){
  data_series = 0
  time <- system.time({for (i in 2:N){
  data_series[i] = data_series[i-1] + sample(c(-1, 1), 1)
  }
  })
  return (time)
}

```

```{r}
#My Codes:
test_new_codes <- function(N){
  set.seed(123)
  steps <- sample(c(-1, 1), N, replace = TRUE)
  data_series = 0
  time <- system.time({for (i in 2:N){
  data_series[i] = data_series[i-1] + steps[i-1]
  }
  })
  return (time)
}
```

```{r}
#TEST:
N1 <- 1000
N2 <- 10000
N3 <- 1000000
test1 <- c(test_original_codes(N1), test_new_codes(N1))
test2 <- c(test_original_codes(N2), test_new_codes(N2))
test3 <- c(test_original_codes(N3), test_new_codes(N3))
test1
test2
test3
```






